---
title: "PANCAN24"
output:
  html_document:
    toc: yes
---

Load all dependecies
```{r, echo=FALSE}

library(gplots)
library(data.table)

source('~/Documents/PhDProjects/GFRN_signatures-master/Key_ASSIGN_functions_balancedsig.R', echo=TRUE)
PANCAN_dir = "~/Documents/PhDProjects/PANCAN24_Analysis/Data/"
outFile= "~/Documents/PhDProjects/PANCAN24_Analysis/Data/PANCAN24data.rda"

#
#pancan12_mutation<-read.csv("~/Documents/PhDProjects/PANCAN24_Analysis/Data/pancan_cleaned_fi

# Read in the pathway predictions from all the cancer types, #short names
setwd("~/Documents/PhDProjects/PANCAN24_Analysis/Data/PathwayPredictions/")
system("ls", intern=TRUE)
filenames<-system("ls", intern=TRUE)
filenames
var_name_all=NULL
  for(i in 1:24){
    ###reading in the filess one at a time
    f<-read.csv(filenames[i], header=1,row.names=1)
    f=as.matrix(f)
    f=f[,c(3,6,8)]
    cancer_type=paste( "(", gsub('\\..*$','',filenames[i]), ")",sep=(''))
    sigature_name=gsub('\\_.*$','',colnames(f))
    #colnames(f)<-paste(toupper(sigature_name), cancer_type, sep=(''))
    colnames(f)<-toupper(sigature_name)
    colnames(f)[2]="KRAS"
    row.names(f)=substr(row.names(f), 1,15)
    var_name=paste("predictions",gsub('\\..*$','',filenames[i]), sep=('_'))
    var_name_all=c(var_name_all,var_name)
    assign(var_name, f)
    }

```


Read in the mutation data
```{r}
setwd("~/Documents/PhDProjects/PANCAN24_Analysis/Data/MutationData/")
filenames_mut=system("ls *.txt", intern=TRUE)
length(filenames_mut)
filenames_mut

filenames_mut[3]
var_name_all_pred_mut=NULL
for (i in 1:24){
  cancerName=paste( "", gsub('\\_.*$','',filenames_mut[i]), "",sep=(''))
   cancerName
  mut_file= read.table(filenames_mut[i], header=1,row.names=1, skip=1)
  rownames(mut_file)
  class(mut_file)
  predFile=paste("predictions_", cancerName, sep = "")
  predFile
  predFile=get(predFile)
  head(predFile)
  dim(predFile)
  rownames(predFile)
  predFile=as.data.frame(predFile)
  class(predFile)
  head(predFile)
  preds_muts=merge(predFile, mut_file, by=0)
  head(preds_muts)
  colnames(preds_muts)=c("Samples","EGFR", "KRAS", "RAF", "BRAF_gene", "EGFR_gene","KRAS_gene")
 preds_muts[5:7]
  preds_muts[5:7] <- lapply(preds_muts[5:7], as.character)
preds_muts[5:7][preds_muts[5:7]=="NaN"]<-"Not Mutated"
preds_muts[5:7][preds_muts[5:7]!="Not Mutated"]<-"Mutated"
preds_muts
var_name=paste("pred_muts",cancerName, sep=('_'))
var_name_all_pred_mut=c(var_name_all_pred_mut,var_name)
assign(var_name, preds_muts)
print(i)
}

dim(pred_muts_HNSC)
dim(pred_muts_READ)
dim(pred_muts_UCS)
dim(pred_muts_LUAD)
dim(pred_muts_OV)
dim(pred_muts_BRCA)
dim(pred_muts_KIRP)
dim(pred_muts_KIRC)
dim(pred_muts_BLCA)

save.image(outFile)


```



# non-function
muts_LAML=read.table(filenames_mut, header=1,row.names=1, skip=1)
View(muts_LAML)
row.names(predictions_LAML)
row.names(muts_LAML)
LAML_preds_muts=merge_drop(predictions_LAML, muts_LAML)
colnames(LAML_preds_muts)
colnames(LAML_preds_muts)=c( "EGFR", "KRAS", "RAF", "BRAF_gene", "EGFR_gene", "KRAS_gene")
dim(LAML_preds_muts)
LAML_preds_muts[4:6] <- lapply(LAML_preds_muts[4:6], as.character)
LAML_preds_muts[4:6][LAML_preds_muts[4:6]=="NaN"]<-"Not Mutated"
LAML_preds_muts[4:6][LAML_preds_muts[4:6]!="Not Mutated"]<-"Mutated"


filenames_mut[1]

View(predictions_ACC)


